ection{Relevant Projects}
\begin{itemize}

 \item \textbf{Weenix Kernel} | \textbf{C}\\
In this project, I worked on building blocks of Weenix operating system such as processes, threads, context switching and synchronization primitives. I also have implemented a Virtual File System (VFS) which provides a common interface between operating system kernel and various file systems and Virtual Memory(VM) which provides an abstraction of address space for user processes.

 \item \textbf{AI Messenger Bot} | \textbf {Node.js, Heroku }\\
 In this project, I built a messenger bot to get details of any professor's University ratings, comments, quality through RateMyProfessor API.Facebook Messenger platform was used which enables bots to converse with users through Facebook Apps and on Facebook Pages.
 
 \item \textbf{Traffic Simulator} | \textbf{C}\\
In this project, I simulated a traffic shaper which transmits packets controlled by a token bucket filter using multi-threading within a single process. All statistics of the packet such as inter-arrival time, service time, average number of packets in a queue, the standard deviation for time spent for a packet along with packet/token drop probability are shown for both input parameters and trace driven mode. 

 \item \textbf{Connect+} | \textbf{HTML, CSS, JavaScript, PHP, MySQL}\\
This is a social networking site used to connect among college peers and friends. The application provides features such personal messaging a friend connected to you, post on their wall, status updates and create groups of people with common interests and pages with relevant interests.

 \item \textbf{PyEdit} | \textbf {Python, PyGtk} \\
This is a word processor in python language using the PyGTK module which includes all features of a text editor along with syntax highlighting of several languages.

 \item \textbf{Zmq Sockets} | \textbf { Python, Zmq}\\
 This is an application to demonstrate messaging patterns (push-pull, request-reply), where a client from a city subscribes to get weather updates from a server with one of these patterns. Zmq socket library was used to implement these functionalities.
 
\end{itemize}
\vspace{5pt}
