\cvsection{Experience}
\begin{cventries}
  \cventry
    {Software Engineer}
    {Samsung Research Institute Bangalore}
    {Bangalore, India}
    {July 2015 - July 2016}
    {
      \begin{cvitems}
        \item {Worked on an automated caching software tool called Autocache.}
        \item {Built the web user interface for the Autocache stand-alone application using Prototype framework .}
        \item {Involved in design and implementation of the flushing the cached data into the hard drive.}
        \item{Helped in setting up debug environment for kernel debugging in RHEL and setup continuous integration tool called Jenkins to automate build and unit testing for the project.}        
      \end{cvitems}
    }      
  \cventry
    {Software Development Intern}
    {}
    {}
    {May 2014 - July 2014}
    {
      \begin{cvitems}
        \item {Built an user interface in Java Swing to automate SD card qualification testing.}
        \item{Tests can be run on multiple devices in parallel and faster along with report generation.}
        \item {Developed a lab management tool to reserve lab or conference rooms within the company for meetings or discussions.}
        \item{Application was integrated with the Samsung SQL database along with IIS Server.}
      \end{cvitems}
    }
    
    \cventry
    {Bilent Services Private Limited}
    {Engineering Intern}
    {Bangalore, India}
    {May 2013 - July 2013}
    {
      \begin{cvitems}
        \item{Worked on website development of an e-commerce service called Kyash.}
        \item {Handled the python based database using NDB Datastore in Google Appengine.}
      \end{cvitems}
    }
\end{cventries}
\vspace{-0.2cm} 