\cvsection{Projects}
\begin{cventries}
%\cventry
 %  {Academic Project in Artificial Intelligence.}
  %  {Game Intelligence Using Adversarial Search}
   % {Los Angeles, California}
    %{September 2016}
    %{
     % \begin{cvitems}
      %  \item {Implemented a project on Game Intelligence Using Adversarial Search.}
       % \item{Involved skills in Java, Recursions, Pruning and Search Algorithms.}
      %\end{cvitems}
    %}
  \cventry
    {built an ai based bot for facebook messenger}
    {AI Messenger Bot}
    {Los Angeles, United States}
    {November 2016}
    {
      \begin{cvitems}
        \item {Built a messenger bot to get details of any Professor's University ratings, comments, quality through RateMyProfessor API.}
        \item {Facebook Messenger platform was used which enables bots to converse with users through Facebook Apps and Pages.}
        \item{Custom intent messages to be replied was developed in Node.js}
      \end{cvitems} 
    }
    \cventry
    {built a slack Bot with node.js microservices}
    {}
    {}
    {January 2017}
    {
      \begin{cvitems}
        \item {Built a resilient, micro-serviced based natural language aware Bot for Slack app with Node.js. }
        \item{Implemented wit.ai Natural Language Processing (NLP) module to process input context to reply corresponding services.}
        \item{ For example, asking a time of any particular location the bot uses google geocoding and timezone API to get corresponding time and is sent back to the user in the chat.}
      \end{cvitems} 
    }
    \cventry
    {weenix kernel}
    {Operating Systems}
    {Los Angeles, United States}
    {August 2016 - November 2016}
    {
      \begin{cvitems}
        \item { Implemented features like processes, threads, context switching and synchronization primitives on Weenix Operating System.}
        \item {Implemented a Virtual File System (VFS) which provides a common interface between OS kernel and various file systems.}
        \item {Implemented Virtual Memory(VM) which provides an abstraction of address space for user processes.}
      \end{cvitems} 
    }
\end{cventries}