\section {Projects}
\begin{itemize}


 \item \textbf{Machine Learning} \\
 - Implemented linear regression, multinomial logistic regression and KNN using Python Numpy libraries. \\
 - Calculated the accuracy of each algorithm on the UCI Wine Quality dataset and MNIST datasets.\\
 - Developed a multi-layer perceptron neural network with relu and softmax non-linearities. \\
 - Implemented K-means algorithm to perform clustering and Gaussian mixture model for density estimation.\\
 - Developed a binary classifier on email dataset from Enron investigation using Naive Bayes classification.

 \item \textbf{Slack Bot} \\
 - Developed a resilient, micro-service based natural language aware bot for Slack app.\\
 - Integrated NLP module wit.ai, to invoke updated query parameters based on application.\\
 - Implemented geocoding and time calculations and also monitoring services. 

  \item \textbf{Parser} \\
 - Built a constituency parser trained from ATIS portion of Penn Treebank.\\
 - Constructed a grammar from the binary trees along with individual probabilites and most frequent rules. \\
 - Implemented CKY algorithm to parse input sentences with grammar and evaluated its F1 score.

  \item \textbf{Limerick Detector} \\
 - Built a limerick detector for the poem of form AABBA line pattern using Python.\\
 - Given data is tokenized and processed using NLTK corpus cmu dict.\\
 - Count of syllables are used to match rhyming words ending in each line.

 \item \textbf{Finite State Automata} \\
 - Developed Soundex calculator, a phonetic algorithm  from NLTK Finite State Transducers.\\
 - It is used to represent and store names as pronounced in English.\\
 - Constructed an FST to translate given Arabic numeral into corresponding French string.

 % \item \textbf{Author Identity} \\
 % - Implemented authorship identification on lines of peotry written by the corresponding authors.\\
 % - Improved the accuracy of Naive Bayes classifier by performing feature engineering.


\end{itemize}
%\vspace{9pt}
